\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{graphics,color} % for pdf, bitmapped graphics files
\usepackage{subfigure}
\usepackage{rotating}
\usepackage{algorithmic}
\usepackage{comment}
\usepackage{algorithm,amssymb,url}
\usepackage{epsfig}
\usepackage[cmex10]{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{cite}
\usepackage{textcomp}

\newboolean{showcomments}
\setboolean{showcomments}{true}

\ifthenelse{\boolean{showcomments}}
{ \newcommand{\mynote}[2]{
    \fbox{\bfseries\sffamily\scriptsize#1}
    {\small$\blacktriangleright$\textsf{\emph{#2}}$\blacktriangleleft$}}}
{\newcommand{\mynote}[2]{}}


\newcommand{\cdu}[1]{\mynote{Corentin}{#1}}
\newcommand{\todo}[1]{\mynote{TODO}{#1}}

\newcommand {\0} {\mathbf 0}
\newcommand {\1} {\mathbf 1}
\newcommand {\bt} {{\mathbf t}_c}
\newcommand {\bb} {{\mathbf b}}
\newcommand {\bx} {\mathbf x}
\newcommand {\eeq} {\end{equation}}
\newcommand {\barr} {\begin{array}}
\newcommand {\earr} {\end{array}}
\newcommand {\bear} {\begin{eqnarray}}
\newcommand {\wU} {\widehat U}
\newcommand {\namep} {Cloud4IoT\relax}
%\thispagestyle{plain}

\begin{document}

\title{Green IoT for developing countries}


\author{
Authors\\
FBK Create-Net, via alla Cascata 56/D, 38123 Trento, Italy.\\
\texttt{<xxx>@fbk.eu}
}

\maketitle

\begin{abstract}
- high development of IoT. IoT is also an enabler technology for IA.
- low development of IoT in third world countries
- high rate of changes in agriculture, with climate change
- IoT is needed to address those chalenges
We show how IoT can meet African challenges, with low cost and low energy consumption hardware.
We demonstrate the use of this technology in a use case where IoT is use to monitor water in Senegal.

\end{abstract}

\begin{IEEEkeywords}
IoT, Energy management, Cloud computing 
\end{IEEEkeywords}

\section{Introduction}
\label{intro}

In this article, we present in Section \ref{iot} the new technologies and trends contributing in making IoT available at a much lower cost for worldwide adoption.
Then, we present in Section \ref{platform} the EU H2020 WAZIUP IoT platform targeting deployment of low-cost IoT and Big Data in developing countries, addressing the aforementioned major issues.
Section \ref{conclu} concludes the article.

\section{State of the Art}
\label{sota}

\section{Green IoT hardware}
\label{iot}


\section{A Cloud platform to support green IoT}
\label{platform}

\section{Use case: water saving in Senegal}
\label{usecase}

\section{Conclusion}
\label{conclu}


\section*{Acknowledgment}
This research received funding from the European Union's H2020 Research and Innovation Action under grant agreement n. 688088 (project AGILE) and grant agreement n. 687607 (project WAZIUP).

\bibliographystyle{IEEEtran}
\bibliography{central-bibliography/bibliography}

\end{document}


